Wiggling the bandwidth

### 2023-01-28 paper.tex
add conclusions and strange effect appendix

% questions
Summing up, here is the questions we aim to provide experimental 
evidence for:
\begin{enumerate}
    \item How close are wiggled estimators and standard estimators with 
        the wiggle bandwidth? 
        What is the radius of $\gamma$'s around $\gamma_0$ such that one 
        can move knowledge from one to the other? 
        How to choose the wiggle range $\Gamma$?
    \item What would be a good point to split the training set in the 
        context of wiggle search?
        When does wiggle search provide an advantage over standard 
        estimators (or if at all)?
    \item Does an iterated wiggle search find the best bandwidth?
        Is it less expensive than classical model selection techniques?
    %\item Given that we move away from the interpolating state 
    %    (in a smooth and controlled manner) does wiggling compare to 
    %    Tikhonov?
    %    What happens with the norm/complexity of a wiggled estimator
    %    compared to the standard one?
\end{enumerate}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{iterative_algo}
    \caption{iterative algo}
    \label{fig:iterative_algo}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Experiment: Does it compare to Tikhonov?}
%

@@

Finally, I propose a list of todos and questions for further research on 
the method.
\begin{itemize}
    \item How far is the reach of wiggling being indicative about the refit
        performance? That is, if I fix an initial bandwidth $\gamma_0$, 
        what is the range of $\gamma$ such that the performance of the 
        estimator $f_{\gamma_0, \gamma}$ can predict that of the estimator
        $f_\gamma$? In small logarithmic local ranges our experiments have
        shown strong similaritity of the risk curves but how far can this be 
        streched? Here, theoretical guarantees are needed to make the method
        pratically usable.
    \item The MNIST dataset have been shown in \cite{justinterpolate} to 
        be predicted best by ridgeless kernel estimators.
        How do the curves from the Tikhonov experiments look like on 
        datasets in which Tikhonov regularization is needed for better
        generalization?
    \item The part I am most interested in would be to prove high-probability
        bounds for the wiggled estimators and potentially convergence rates
        for the iterative algorithm (as it seems to be quite fast).
        Luckily, I am working in a research group (MaLGa in Genova) that 
        have very good understanding of kernel matrices of Matérn kernels
        and have already proven many bounds for kernel ridge(less) 
        regression in the past.
    \item Most importantly: check the literature for any papers on these
        methods. I haven't found anything so far but my research was not 
        extensive.
\end{itemize}

>>>>

% questions
Summing up, here is the questions we aim to provide experimental 
evidence for:
\begin{enumerate}
    \item How close are wiggled estimators and standard estimators with 
        the wiggle bandwidth? 
        What is the radius of $\gamma$'s around $\gamma_0$ such that one 
        can move knowledge from one to the other? 
        How to choose the wiggle range $\Gamma$?
    \item What would be a good point to split the training set in the 
        context of wiggle search?
        When does wiggle search provide an advantage over standard 
        estimators (or if at all)?
    \item Does an iterated wiggle search find the best bandwidth?
        Is it less expensive than classical model selection techniques?
\end{enumerate}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{iterative_algo}
    \caption{Iteratively applying wiggle search and then refitting
        a standard estimator with the found optimal bandwidth.}
    \label{fig:iterative_algo}
\end{figure}

@@

@@

This paper proposes two new methods for leveraging the bandwidth in 
Laplacian kernel ridgeless regression.
The results seem to indicate that there is potential for them to replace
classical methods for optimizing the parameter (grid search, 
cross-validation) as they are expensive and don't scale well to big data.
The methods have been demonstrated to improve over standard estimators 
in some cases even with nearly optimal bandwidth guess.
However, much further experimentation is necessary and providing 
theoretical guarantees is thinkable as the recent progresses in the field 
have opened new doors.

Finally, I add a list of todos and questions for further research on 
the method.
\begin{itemize}
    \item Bigger scale experiments are necessary to prove that the method
        really scales well (my computer couldn't do it)
        Also because the MNIST dataset have been shown in \cite{justinterpolate} 
        to be predicted best by ridgeless Laplacian estimators.
        What happens with more noisy datasets?
    \item Given that we move away from the interpolating state 
        (in a smooth and controlled manner) does wiggling compare to 
        Tikhonov?
        What happens with the norm/complexity of a wiggled estimator
        compared to the standard one?
    \item As a mathematician I really want to leave the experimental world
        and analyze on paper providing risk bounds.
        There is in particular one phenomenon that I found by mistake and 
        that I couldn't label.
        If it is a general rule, that would imply that a wiggled estimator
        "knows" about the the standard estimator and can be used to find its 
        global risk minimum (always w.r.t. the bandwidth).
        See \cref{app:strange}.
    \item Check the literature for any papers on these
        methods. I haven't found anything so far but my research was not 
        at all exhaustive.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{A strange effect} \label{app:strange}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{strange}
    \caption{Strange: Cheap wiggled estimators seems to know the expensive 
        standard ones perfectly well?}
    \label{fig:strange}
\end{figure}

In one of my other experiments I used the inverse bandwidth convention.
It is more or less the same plot as in \cref{fig:range} just with 
$\gamma \to 1/\gamma$ so that I had to manually edit the bandwidth 
values to obtain readable results in the new scale.
However, in that inverse, it appeared to me that the wiggled estimator
"knew" perfectly well where the true optimal bandwidth of the standard 
estimator is.
Indeed, \cref{fig:strange} shows extrema at exactlt that best point 
even if the base bandwidth is far away.
I coudln't confirm that this is a big coincidence but I would like to 
investigate that more.
